Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
Done with the rough draft. It is very rough, but also very done.

\subsubsection{Data Type}
(REDO)

@@

More text.

\subsubsection{Data Recipient}
(REDO)

@@

\subsubsection{Device Type}

@@

>>>>

\subsubsection{Data Type}
(REDO) Okay, I list all of the top 10/bottom 10 lists I generated: the one for all recipients, one only with respect to friends, work, and public, and another for the app only. I think the interesting thing to do is to show the shared vs app only lists, and to highight what is different. If I could show the whole list of 70+ for both, that would be most insightful, but I don't have the place for it in this paper, so this will have to do. Maybe I can do a top/bottom 15 at the least, maybe that will be better?

@@

Results were that in the top 10, both app only and shared had: bank info, SSN, PIN, embarassing photo, naked photo, naked video. Write a sentence on why I think that is here. The differences were that the app had: door pw, sex freq, embarssing videos, and photos at home, while the shared had the differing top 5 to be work conversations, credit card, username and password,  and phone conversations. It's cool to see that it's like one is talking to a machine or a company and the other to a person, right?

In the low 10, the common 6 were exercise details, age, tv shows, gender, heart rate, and language. For the 4 different low 10, the app only had: phone use, how much you like people, when and what you ate, and eye patterns for tracking. For shared, these 4 were name, having fun or happy, music, and if a person was busy or interruptible. Also, this is interesting. People don't want to share phone use, opinions on people, food habits, or eye patterns, but would find it useful to have for apps, and well, people don't care about observable things or happy/music with people. But maybe not apps since it seems creepy or will give them ads.

\subsubsection{Data Recipient}
(REDO) Data recipient matters in how upset people get, or well, how much their privacy is invaded and even how secure their information is. What really matters is if it is shared to people or not. There isn't much difference between the friends, work, and public--they are all quite upsetting. Friends is a little lower, but not too significantly (do stats-y thing here). The difference between public being lower than work is probably due to the fact that people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared. Basically, what matters is that there are guarantees that the information is bounded and used in a way that people would assume it would be used.

@@

\subsubsection{Device Type}
(REDO) So, there is a difference between the device types, but I need to do more work to see if this is statistically significant or not. In either case, this matters the least, and device type and data recipient are more influencing factors. This is just the result of biases in people we can't quite quantify.

@@

with upset rates (cubetastic upset rate | smartphone upset rate)\\
Q1: (14.81\% | 6.13\%)\\
Q2: (44.11\% | 19.85\%)\\
Q3: (87.09\% | 58.44\%)\\
Q4: (52.77\% | 55.79\%)\\
Q5: (86.49\% | 91.82\%)

Exact question details here, and statistical stuff. Conclude with whatever conclusion I happen to come to after performing the statistical analysis.
